---
title: "Analyze FARS"
author: "Max Eisholer"
date: "11.05.2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analyze FOR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Description

This package allows you to read and analyze the annual Fatality 
Analysis Report of fatal injuries suffered in motor vehicle                  traffic crashes. You can summarize the fatalaties for each year              or range of years and you can draw state maps for the locations              for each fatal injury in each year. Load the package using:
```{r setup}
library(courserapackage)
```

### Usage

Download the FAR files you want to analyze and store them in your working
directory. Alternatively you can use theire respective path in the following functions call.
Use 
```
fars_read_years(years)
```
if you want to see the dataset for the year or the range of years. If you want 
to get a summary of fatal injuries in car accidents for oce year or a range of 
years by month use.

```
fars_sunmmarize_years("2005:2013")
```

Finally you can draw state maps of the location of each fatal injury in a year
using:
```
fars_map_state("1","2013")
```
It takes the state number and the year as Input. Refere to the [NCSA Documentation](https://crashstats.nhtsa.dot.gov/#/DocumentTypeList/23) for the
state numbers.


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
